Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates Affect Rice Sheath Blight?

### 2018-04-26 analysis/paper/paper.Rmd
Update static docs

For each measurement, e.g. 2015 tiller incidence, 2016 tiller incidence, a single MCMC chain was run for 55,000 steps, with the first 5000 discarded as burn in. The remaining 50,000 samples were thinned by taking every tenth sample, resulting in 5000 independent draws from the posterior distribution of the parameters of the model.

@@

In 2016 the N180 treatment was significantly different from the N60 treatment, with N180 severity being higher. The AWD water management, which was lower than FLD, was also significantly different.

@@

All data generated from this project and code used for analysis are available as a research compendium from <https://github.com/openplantpathology/rice_awd_pests> with instructions on how to cite the compendium and use the Docker file to recreate the full analysis and this manuscript [@Sparks2018].

>>>>

For each measurement, e.g. 2015 tiller incidence, 2016 tiller incidence, a single MCMC chain was run for 55,000 steps, with the first 5000 discarded as burn in. The remaining 50,000 samples were thinned by taking every tenth sample, resulting in 5000 independent draws from the posterior distribution of the parameters of the model. The model

@@

In 2016 the N180 treatment was significantly different from the N60 treatment, with N180 severity being higher. The AWD water management, which was lower than the FLD treatment, was also significantly different.

@@

All data generated from this project and code used for analysis are available as a reproducible research compendium from <https://github.com/openplantpathology/rice_awd_pests> [@Sparks2018].
